The title

### 2024-10-04 05_Manuscript/manuscript.Rmd
adding trackdown

@@

@@

efa_loadings <- as.data.frame(unclass(EFA_fit$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.))

@@

>>>>

```{r trackdown, eval = F}
library(trackdown)
# upload_file(
#   file = "manuscript.Rmd",
#   gfile = "gen_scale_manuscript_trackdown",
#   gpath = "gen_scale/",
#   hide_code = TRUE
# )

# pull to me 
download_file(
  file = "manuscript.Rmd",
  gfile = "gen_scale_manuscript_trackdown",
  gpath = "gen_scale/",
  hide_code = TRUE
)

# push to google
update_file(
  file = "manuscript.Rmd",
  gfile = "gen_scale_manuscript_trackdown",
  gpath = "gen_scale/",
  hide_code = TRUE
)
```

@@

also do five

@@

# remember you gotta fix this because of the order of operations 
efa_loadings <- as.data.frame(unclass(EFA_fit$loadings)) %>% 
  mutate(keep = ifelse(
    ML1 >= .30, "yes", ifelse(
      ML2 >= .30, "yes", ifelse(
        ML1 >= .30 & ML2 >= .30, "no", "no"
      )
    )
  )) %>% 
  mutate(question = rownames(.))

@@

```{r}
EFA_fit <- fa(efaDF, #data
              nfactors = 5, #number of factors
              rotate = "oblimin", #rotation
              fm = "ml") #math

efa_loadings <- as.data.frame(unclass(EFA_fit$loadings)) %>% 
  mutate(question = rownames(.)) %>% 
  rowwise() %>%
  mutate(keep = sum(c_across(-question) >= .30)) %>% 
  ungroup()

EFA_fit_2 <- fa(efaDF %>% 
                  select(efa_loadings %>% 
                           filter(keep == 1) %>% 
                           pull(question)), #data
              nfactors = 5, #number of factors
              rotate = "oblimin", #rotation
              fm = "ml") #math

efa_loadings_2 <- as.data.frame(unclass(EFA_fit_2$loadings)) %>% 
  mutate(question = rownames(.)) %>% 
  rowwise() %>%
  mutate(keep = sum(c_across(-question) >= .30)) %>% 
  ungroup()

EFA_fit_3 <- fa(efaDF %>% 
                  select(efa_loadings_2 %>% 
                           filter(keep == 1) %>% 
                           pull(question)), #data
              nfactors = 5, #number of factors
              rotate = "oblimin", #rotation
              fm = "ml") #math

EFA_fit_3

efa_loadings_3 <- as.data.frame(unclass(EFA_fit_3$loadings)) %>% 
  mutate(question = rownames(.)) %>% 
  rowwise() %>%
  mutate(keep = sum(c_across(-question) >= .30)) %>% 
  ungroup()

- take the final version of each "best model" 
- get down to 5 items each or whatever is left (best loading and theoretical)
- look at the fit indices to tell which may be best
